---
title: "Tutorium_28_05_PreProj_Part2_Sample selection"
author: "dzt"
date: "5/27/2021"
output: pdf_document
---

The Middle part of the project.

New Thema:

-Sample selection, using regsubsets() function


 


#  1 Daten import

```{r}
library(readr)
research <- read_csv("https://raw.githubusercontent.com/sebastiansauer/willingness-vaccination-covid19/main/data/d3.csv")

```


`

# 2 Check the missing number
```{r}
library(skimr) 
skim(research) 
```

2 age missing

```{r}
library(dplyr)
research <- select(research, -extra,-agree,-neuro,-cons,-open)
research
```

# 3 Drop cases with missing values in age


```{r}
library(tidyr)
researchnona1 <-
research %>%drop_na(age) 

skim(researchnona1)
```
```{r}
researchnona1
```

#  4 Distribution of output "willingess" variablen
```{r}
library(ggplot2)
researchnona1%>%
ggplot(aes(x=willingness)) + geom_histogram()
```

#  5 Reshaping the data(pivot_long)


```{r}

library(tidyverse)
researchreshaping <-
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable")
  # everything() is a convenient shorthand to pivot all variables. pivot_longer(everything()) https://jhudatascience.org/tidyversecourse/wrangle-data.html

researchreshaping
```


#  6 Distribution of all predictors 

```{r}

  ggplot(researchreshaping,aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")
```
For both the cases variables, the right-skew makes the lower end of the x-axis hard. 
To make patterns in the data more interpretable and for helping to meet the assumptions of inferential statistics, then need to be transformed


# 7 How to transform data to normal distribution in R?  

<https://www.datanovia.com/en/lessons/transform-data-to-normal-distribution-in-r/>
<https://moderndive.com/11-thinking-with-data.html#house-prices-EDA-I> 11.3

first try log transformation in a situation where the dependent variable starts to increase more rapidly with increasing independent variable values

log10(x) for positively skewed data,
log10(max(x+1) - x) for negatively skewed data


#  8 Transform  (via logarithm)

```{r}

researchnona1<- mutate(researchnona1,cases_log10=log10(age)) 
researchnona1
```


```{r}
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable") %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")#Each axis has a scale
```

  
# 9  Check outliers
```{r}
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable") %>%
  ggplot(aes(x = value)) +
  geom_boxplot() +
  facet_wrap(~ variable, scales = "free")
```
  

# 10 Find correlation (cormatrix)
```{r}
library(corrplot)
researchnona1 <- select_if(researchnona1, is.numeric)
corrplot(cor(researchnona1), method = "circle")
```
cases_log10 and age have a strong positive correlation



```{r}
cor(researchnona1)
```

Creat models, willingness as outcome, to see which variables can be used in model
# 11 Model 1
```{r}
model1 <- lm(willingness ~ fear, data = researchnona1)
```

# 12 Model 2
```{r}
model2 <- lm(willingness ~ fear+cons1, data = researchnona1)
```

# 13 Model 3
```{r}
model3 <- lm(willingness ~ fear + cons1 + cons2, data = researchnona1)
```

# 14 The regsubsets() function 
(part of the leaps library) performs best subregsubsets()
set selection by identifying the best model that contains a given number
of predictors, where best is quantified using RSS
From: ISLR Book 6.5
```{r}
library (leaps)
modelfull <- regsubsets (willingness ~.,researchnona1)
summary (modelfull)
```
An asterisk indicates that a given variable is included in the corresponding
model. For instance, this output indicates that the best two-variable model
contains only fear and cons1. By default, regsubsets() only reports results
up to the best eight-variable model

# 15 The regsubsets() function,examine R2, RSS, adjusted R2, Cp, and BIC
```{r}
reg.summary =summary (modelfull)
names(reg.summary)
```
# 16 Check adjust r squared
```{r}
reg.summary$adjr2
```
For instance, we see that the R2 statistic increases from 15.8%, when only
one variable is included in the model, to almost 28.2 %, when all variables
are included. As expected, the R2 statistic increases monotonically as more
variables are included.


```{r}


plot(reg.summary$adjr2 ,xlab =" Number of Variables ",
ylab=" Adjusted RSq",type="l")
```
`

# 17 Confirm model 
extra1 extra2
```{r}
model4 <- lm(willingness ~fear + extra1+ agree1+ cons1 +open1 +extra2  +neuro2 + open2  ,data = researchnona1 )
```

```{r}
summary(model4)
```
# 18 Confirm model with interaktion
```{r}
model5 <- lm(willingness ~fear + extra1+ agree1+ cons1 +open1 +extra2  +neuro2 + open2 + fear:cons1+ fear:extra2  ,data = researchnona1 )
```

```{r}
summary(model5)
```

