

```{r}

library(tidyverse)
```

```{r}
read.csv()
```



## Overview
check first 6 lines of the dataset
```{r}
head(loans_full_schema)
```

```{r}
skim(loans_full_schema)
```
        
##  Dataset division in Train and Test


select only 1000 lines of data
```{r}
loans_full_schema <- loans_full_schema %>%
  slice(1:1000)
loans_full_schema
```

```{r}

train <-  slice_sample(loans_full_schema, prop=.75)
train
```



```{r}
test <- anti_join(loans_full_schema, train, by="emp_title")
test
```
##  Train,test data adjustment (only for this dataset case as it is sooo huge)


update the train data contains following variables: verified_income, debt_to_income, issue_month, annual_income, total_credit_utilized and total_credit_limit
```{r}
train <- train %>%
  select(emp_title,interest_rate, verified_income, debt_to_income, issue_month,annual_income,total_credit_utilized, total_credit_limit) 
train
```

```{r}

test <- test %>%
  select(emp_title,interest_rate, verified_income, debt_to_income, issue_month,annual_income,total_credit_utilized, total_credit_limit) 
test
```



##  Drop Missing values which are not so much large amount compare to the whole sample (<10%)

```{r}
skim(train)
```


```{r}
train <- 
  train %>%
  drop_na(debt_to_income )

```
`



##  Reshaping the data (pivot_longer)
```{r}
pivot <-
select_if(train,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable")
  # everything() is a convenient shorthand to pivot all variables. pivot_longer(everything()) https://jhudatascience.org/tidyversecourse/wrangle-data.html
pivot
```


## Check outliers in outcome (interest_rate)  using boxplot
```{r}
pivot %>%
  ggplot(aes(x = value)) +
  geom_boxplot() +
  facet_wrap(~ variable, scales = "free")
```

## Check outliers in outcome(interest_rate) using Z value


z=(x-mean)/sd
```{r}
outliers<-
train %>%
mutate(interestrate_z = (interest_rate - mean(interest_rate, na.rm = TRUE)) /
sd(interest_rate, na.rm = TRUE)) %>%
mutate(is_extreme = if_else(abs(interestrate_z) > 3, TRUE, FALSE)) %>%
count(is_extreme)
```


```{r}
outliers
```
TRUE: outliers
FALSE : not outliers




## Drop outliers in outcome (filter)
```{r}
train_outliers <- train%>%mutate(interestrate_z = (interest_rate - mean(interest_rate, na.rm = TRUE)) /
sd(interest_rate, na.rm = TRUE)) %>%
mutate(is_extreme = if_else(abs(interestrate_z) > 3, TRUE, FALSE))
train_outliers
```





```{r}
train <-
  train_outliers %>% 
  filter(is_extreme==FALSE)
train
```

##  Distribution of outcome

```{r}
train%>%
ggplot(aes(x=interest_rate)) + geom_histogram()
```

##  Distribution of all predictors 

```{r}

  ggplot(pivot,aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")
```

## Transform  (via logarithm)
```{r}
train<- train%>%
  mutate(annual_income_log10=log10(annual_income),total_credit_limit_log10=log10(total_credit_limit))
train
```

```{r}
train_new <- train%>% select(-interestrate_z,-emp_title)
train_new
```



#  Model
##  The regsubsets() function  (best sample)
(part of the leaps library) performs best subregsubsets()
set selection by identifying the best model that contains a given number
of predictors, where best is quantified using RSS
From: ISLR Book 6.5


```{r}
library (leaps)
model <- regsubsets (interest_rate ~., train_new, really.big=T)
summary (model)
```

```{r}

reg.summary =summary (model)
names(reg.summary)
```


```{r}
reg.summary$adjr2
```
## Model1
```{r}
model1 <- lm(interest_rate ~ verified_income + debt_to_income + total_credit_utilized +total_credit_limit+ annual_income_log10 + total_credit_limit_log10  ,data = train_new )
```

```{r}
summary(model1)
```
## Model2
```{r}
model2 <- lm(interest_rate ~ verified_income + debt_to_income + total_credit_utilized +total_credit_limit+ annual_income_log10 + total_credit_limit_log10 + total_credit_utilized:verified_income ,data = train_new )
summary(model2)
```


#  Prediction

## log transform also in test data (as in the model contains log vaoriables)
```{r}
test<- test%>%
  mutate(annual_income_log10=log(annual_income),total_credit_limit_log10=log(total_credit_limit))

test
```

```{r}
pred <- predict(model2, newdata = test)
head(pred)
```


```{r}
test2 <- mutate(test, pred)
test2



```

```{r}
handover<- select(test2, pred,emp_title)
handover
```


