---
title: "Tutorium-18-06-CaseStudy-Seattle house prices"
author: "dzt"
date: "6/18/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
---



This dataset contains house sale prices for King County, which includes Seattle. It includes homes sold between May 2014 and May 2015.

It's a great dataset for evaluating simple regression models.


Dataset is from : <https://www.kaggle.com/harlfoxem/housesalesprediction>

Case Study is here : <https://moderndive.com/11-thinking-with-data.html#seattle-house-prices>


In this case study, we’ll create a multiple regression model where:

The outcome variable y is the sale price of houses.


# EDA
 
 
```{r}
library(tidyverse)
library(moderndive)
library(skimr)
library(fivethirtyeight)
```



## Overview
```{r}
skim(house_prices)

```


##  Reshaping the data (pivot_longer)
```{r}


house_prices_pivot <-
select_if(house_prices,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable")
  # everything() is a convenient shorthand to pivot all variables. pivot_longer(everything()) https://jhudatascience.org/tidyversecourse/wrangle-data.html
house_prices_pivot
```

## Distribution of all predictors 

```{r}

  ggplot(house_prices_pivot,aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")
```



For both the price and sqft_living variables, the right-skew makes distinguishing houses at the lower end of the x-axis hard. This is because the scale of the x-axis is compressed by the small number of quite expensive and immensely-sized houses.

## log10 transformation to right-skew variables

```{r}
house_prices <- house_prices %>%
  mutate(
    log10_price = log10(price),
    log10_size = log10(sqft_living)
    )
```

```{r}
# Before log10 transformation:
ggplot(house_prices, aes(x = price)) +
  geom_histogram(color = "white") +
  labs(x = "price (USD)", title = "House price: Before")

# After log10 transformation:
ggplot(house_prices, aes(x = log10_price)) +
  geom_histogram(color = "white") +
  labs(x = "log10 price (USD)", title = "House price: After")
```

```{r}
# Before log10 transformation:
ggplot(house_prices, aes(x = sqft_living)) +
  geom_histogram(color = "white") +
  labs(x = "living space (square feet)", title = "House size: Before")

# After log10 transformation:
ggplot(house_prices, aes(x = log10_size)) +
  geom_histogram(color = "white") +
  labs(x = "log10 living space (square feet)", title = "House size: After")
```

##  Dataset division in Train and Test
```{r}
train <-  slice_sample(house_prices, prop=.75)
train
```


```{r}
test <- anti_join(house_prices, train, by="id")
test
```
## Check outliers in outcome using Z value

z=(x-mean)/sd
```{r}
train_outliers<-
train %>%
mutate(price_z = (price - mean(price, na.rm = TRUE)) /
sd(price, na.rm = TRUE)) %>%
mutate(is_extreme = if_else(abs(price_z) > 3, TRUE, FALSE)) %>%
count(is_extreme)
```



```{r}
train_outliers
```
TRUE: outliers
FALSE : not outliers
 
 
## Drop outliers in outcome (filter)
```{r}

train_outliers <- train%>%mutate(price_z = (price - mean(price, na.rm = TRUE)) /
sd(price, na.rm = TRUE)) %>%
mutate(is_extreme = if_else(abs(price_z) > 3, TRUE, FALSE))
train_outliers
```


```{r}
train <-
  train_outliers %>% 
  filter(is_extreme==FALSE)
train
```

# Model 1 with transformed predictors (y= log10_price, x1=log10_size, x2=condition)
## Interaction 
```{r}
# Plot interaction model
ggplot(train, 
       aes(x = log10_size, y = log10_price, col = condition)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(y = "log10 price", 
       x = "log10 size", 
       title = "House prices in Seattle")
```


we see there is a positive relationship between house price and size, meaning as houses are larger, they tend to be more expensive.


and with different condition will result differnt slopes of size and price, that is, condition has interaction with size

## Fit regression model with log transformation and interaction
```{r}
# Fit regression model:
price_interaction <- lm(log10_price ~ log10_size * condition, 
                        data = train)

# Get regression table:
get_regression_table(price_interaction)
```
```{r}
summary(price_interaction)
```


# Prediction


```{r}
pred <- predict(price_interaction, newdata = test)
```


## reverse transformation in pred
```{r}
library(modelr)
house_prices <-
  house_prices %>% 
  add_predictions(price_interaction,
                  var = "pred_log10") %>% 
  mutate(pred = 10^pred_log10)
```
<https://data-se.netlify.app/2021/06/18/r%C3%BCcktransformation-logarithmierter-y-werte/>


## check
```{r}
house_prices %>% 
  select(price, pred_log10, pred) %>% 
  slice(1:10)
```

```{r}
test2 <- mutate(test, pred)
```



```{r}
handover<- select(test2, pred,id)
handover
```

