---
title: "Untitled"
author: "dzt"
date: "4/29/2021"
output: html_document
---



# Dplyr and ggplot exercise
## Solve the following tasks only with the dplyr and ggplot2 library. We will repeat the following functions:

filter () (and slice ())\ 
arrange ()\
select () (and rename ())\
distinct ()\
mutate () (and transmute ())\
summarize ()\
sample_n () and sample_frac ()\
reorder()\
corrplot()\


## 1 load dplyr
```{r }
library(dplyr)
```


## 2 We will use the mtcars data frame for this exercise


```{r}
head(mtcars)
```
## 3 Give the row name a column name
```{r}
library(tidyverse)
mtcars <-
rownames_to_column(mtcars, var = "cars")
```

```{r}
head(mtcars)
```

## 4 Output the lines of the cars with an mpg value over 20 and exactly 6 cylinders.

```{r}
mtcars%>%
filter(mpg>20, cyl==6)
```

## 5 Rearrange the data frame. It should first be sorted according to cyl and then in descending order according to wt
```{r}
head(arrange(mtcars,cyl,desc(wt)))
```
## 6 Select the mpg and hp columns.

```{r}
head(select(mtcars,mpg,hp))
```
## 7 Choose the unique values of the gear column.

```{r}
distinct(select(mtcars,gear))
```

## 8  Find the average mpg value using dplyr.
```{r}
avg_mpg <-
summarise(mtcars,mean(mpg))
 avg_mpg
```




## 9 Use the pipe operator to get the average hp value for cars with 6 cylinders.

```{r}
mtcars %>% filter(cyl==6) %>% summarise(avg_hp = mean(hp))
```


## 10 Create a new column "Performance", which is calculated by hp divided by wt.
```{r}
mtcars <-
mtcars %>%
mutate(performance= hp/wt)

mtcars

```
## 11 Which car brand has the best perforamcne?
```{r}
performancelist <-
mtcars %>%
  select(cars,performance) %>%
  arrange(desc(performance))

performancelist
```

## 12 Show the first 10% performance

```{r}
mtcarstop10percent <-
mtcars%>%
  filter(percent_rank(performance)>.9)

mtcarstop10percent
```

## 13 Show the first 10% performance in ggplot

```{r}
library(ggplot2)

ggplot(mtcarstop10percent, aes(x=cars,y=performance)) + geom_bar(stat = "identity")
# If you want the heights of the bars to represent values in the data, use stat="identity" and map a value to the y aesthetic.#
```


## 14 Reorder the bar

```{r}
ggplot(mtcarstop10percent, aes(x=reorder(cars,performance), y=performance))+ 
  geom_bar(stat="identity")


```

`


## 15 Pearson correlation between 2 variables
```{r}

cor(mtcars$hp, mtcars$mpg)
```


## 16 Correlation matrix: correlations for all variables
```{r}
#The function corrplot() takes the correlation matrix as the first argument. 
# because column cars is not a numeric, so we first need to select the all the numeric.

library(corrplot)

mtcarscorplot <- select_if(mtcars, is.numeric)
corrplot(cor(mtcarscorplot), method = "circle")

```









