---
title: "R4DS Chpater3 exercise"
author: "dzt"
date: "4/23/2021"
output: html_document
---

<https://r4ds.had.co.nz/data-visualisation.html>
<https://jrnold.github.io/r4ds-exercise-solutions/data-visualisation.html#introduction-1>


##3.2.4.1

# Run ggplot(data = mpg). What do you see?


```{r}
ggplot(data = mpg)
```


# How many rows are in mpg? How many columns?

```{r}
nrow(mpg)
ncol(mpg)
```


# What does the drv variable describe? Read the help for ?mpg to find out.

the type of drive train, where f = front-wheel drive, r = rear wheel drive, 4 = 4wd

# make a scatterplot of hwy vs cyl.


```{r}
p1<- ggplot(mpg, aes(x=hwy, y=cyl))+geom_point()
p1
```

# What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
```{r}
p2<- ggplot(mpg, aes(x = class, y = drv)) + geom_point()
p2
```
A scatter plot is not a useful display of these variables since both drv and class are categorical variables. Since categorical variables typically take a small number of values, there are a limited number of unique combinations of (x, y) values that can be displayed. In this data, drv takes 3 values and class takes 7 values, meaning that there are only 21 values that could be plotted on a scatterplot of drv vs. class

As such, scatterplots work best for plotting a continuous x and a continuous y variable











##3.3.1

# What’s gone wrong with this code? Why are the points not blue?


The argumentcolour = "blue" is included within the mapping argument, and as such, it is treated as an aesthetic, which is a mapping between a variable and a value. 

In the expression, colour = "blue", "blue" is interpreted as a categorical variable which only takes a single value "blue"

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

```{r}
ggplot(data = mpg,aes(x = displ, y = hwy)) + geom_point(color = "blue")
```


# Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?


```{r}
glimpse(mpg)
```
The following list contains the categorical variables in mpg:

manufacturer
model
trans
drv
fl
class
The following list contains the continuous variables in mpg:

displ
year
cyl
cty
hwy

# Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
ggplot(data = mpg,aes(x = displ, y = hwy,color = cty)) + geom_point()
```
```{r}
ggplot(data = mpg,aes(x = displ, y = hwy)) + geom_point(color = mpg$cty)
```                                                       
```{r}
ggplot(mpg, aes(x = displ, y = hwy, size = cty)) +
  geom_point()
```
```{r}
ggplot(mpg, aes(x = displ, y = hwy, shape = cty)) +
  geom_point()
```
When a continuous value is mapped to shape, it gives an error. Though we could split a continuous variable into discrete categories and use a shape aesthetic, this would conceptually not make sense. A numeric variable has an order, but shapes do not. It is clear that smaller points correspond to smaller values, or once the color scale is given, which colors correspond to larger or smaller values. But it is not clear whether a square is greater or less than a circle.


# What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = hwy, size = displ)) +
  geom_point()
```

In the above plot, hwy is mapped to both location on the y-axis and color, and displ is mapped to both location on the x-axis and size. The code works and produces a plot, even if it is a bad one. Mapping a single variable to multiple aesthetics is redundant. Because it is redundant information, in most cases avoid mapping a single variable to multiple aesthetics.

# What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

Stroke changes the size of the border for shapes (21-25). These are filled shapes in which the color and size of the border can differ from that of the filled interior of the shape.
```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "black", fill = "white", size = 5, stroke = 5)
```


# What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.


```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = displ < 5)) +
  geom_point()
```
In this case, the result of displ < 5 is a logical variable which takes values of TRUE or FALSE.


#3.5.1

# What happens if you facet on a continuous variable?

# What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))

# What plots does the following code make? What does . do?

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
# Take the first faceted plot in this section:

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

# Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?

When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?



#3.6.1

#3.7.1


#3.8.1

#3.9.1
