---
title: "Tutorium_07_05_2021_PreProj_Part1"
author: "dzt"
date: "5/6/2021"
output: html_document
---

The first part of the project.

Thema:

-Data import

-Exploratory data analysis
 -datashape transform(pivot_long())
 -distribution check(ggplot(),facet_wrap())
 -logarithm transformation(log())
 -missing value check(skim(),drop())
 -correlation check (cor())
 -outliers check(boxplot)

-some stories found in the data


 


#  1 Daten import

```{r}
library(readr)
research <- read_csv("https://raw.githubusercontent.com/sebastiansauer/willingness-vaccination-covid19/main/data/d3.csv")

```


`

# 2 Check the missing number
```{r}
library(skimr) 
skim(research) 
```

2 age missing

```{r}
library(dplyr)
research <- select(research, -extra,-agree,-neuro,-cons,-open)
research
```

# 3 Drop cases with missing values in age


```{r}
library(tidyr)
researchnona1 <-
research %>%drop_na(age) 

skim(researchnona1)
```
```{r}
researchnona1
```

#  4 Distribution of output "willingess" variablen
```{r}
library(ggplot2)
researchnona1%>%
ggplot(aes(x=willingness)) + geom_histogram()
```

#  5 Reshaping the data(pivot_long)


```{r}

library(tidyverse)
researchreshaping <-
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable")
  # everything() is a convenient shorthand to pivot all variables. pivot_longer(everything()) https://jhudatascience.org/tidyversecourse/wrangle-data.html

researchreshaping
```


#  6 Distribution of all predictors 

```{r}

  ggplot(researchreshaping,aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")
```
For both the cases variables, the right-skew makes the lower end of the x-axis hard. 
To make patterns in the data more interpretable and for helping to meet the assumptions of inferential statistics, then need to be transformed


# 7 How to transform data to normal distribution in R?  

<https://www.datanovia.com/en/lessons/transform-data-to-normal-distribution-in-r/>
<https://moderndive.com/11-thinking-with-data.html#house-prices-EDA-I> 11.3

first try log transformation in a situation where the dependent variable starts to increase more rapidly with increasing independent variable values

log10(x) for positively skewed data,
log10(max(x+1) - x) for negatively skewed data


#  8 Transform  (via logarithm)

```{r}

researchnona1<- mutate(researchnona1,cases_log10=log10(age)) 
researchnona1
```


```{r}
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable") %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")#Each axis has a scale
```

  
# 9  Check outliers
```{r}
select_if(researchnona1,is.numeric) %>%  # select only numbers
  pivot_longer(everything(), names_to = "variable") %>%
  ggplot(aes(x = value)) +
  geom_boxplot() +
  facet_wrap(~ variable, scales = "free")
```
  

# 10 Find correlation (cormatrix)
```{r}
library(corrplot)
researchnona1 <- select_if(researchnona1, is.numeric)
corrplot(cor(researchnona1), method = "circle")
```
cases_log10 and age have a strong positive correlation



```{r}
cor(researchnona1)
```



# 11 Creat a regression model based on the correlation and transformation
```{r}
cases_interaction <- lm(researchnona1$willingness ~ age + cases_log10 + age *cases_log10 , 
                        data = researchnona1)
summary(cases_interaction)
```


# 12 Interpretation the regression model based on the correlation and transformation

$y =1026.85+ 208.491∗age - 2113.392∗cases_log10 - 93.74* age*cases_log10$



# 13 Plotting Interaction Effects of Regression Models
<https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_interactions.html>

```{r}

library(sjPlot)

```
```{r}
plot_model(cases_interaction, type = "int") #type = "int" to plot marginal effects of interaction terms in a more convenient way.
```

# 14 The relationship between health situation with reserved character in different ages
```{r}
ggplot(researchnona1, 
       aes(x = extra1, y = health)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~age)
```

At age 18 and 23, the reserved character has more effect on health situation, at other ages, seems quite plain


# 15 Willingness to get a covid19 vaccination between genders

```{r}
ggplot(research, 
       aes(x = willingness))+geom_histogram() + facet_wrap(~sex)
```
we can see either girls or boys have more people willing to get a covid19 vaccination



